A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-19 tex/codatadp.tex
minor

\hyphenation{data-type data-types co-data-type co-data-types}

@@

To evaluate the decision procedure, we generated problems from existing
Isabelle formalizations using Sledgehammer \cite{paulson-blanchette-2010}.
Codatatypes being a recent addition to Isabelle
\cite{blanchette-et-al-2014-impl}, benchmarks are somewhat hard to come by. We
included the theory files from the Isabelle distribution (the Distro) and the \emph{Archive
of Formal Proofs} (AFP) \cite{klein-et-al-afp} that define codatatypes falling
within the supported fragment. We also included two unpublished theories by
Peter Gammie and Andreas Lochbihler (\gandl), about Bird and Stern--Brocot trees.
To also exercise the the support
for datatypes, the benchmarks are complemented by theories about various list
and tree data structures. The theory files were selected before running the
experiments. The experimental data is publicly available \cite{our-eval-data}.

>>>>

\hyphenation{data-type data-types co-data-type co-data-types isa-belle sledge-hammer}

@@

To evaluate the decision procedure, we generated problems from existing
Isabelle formalizations using Sledgehammer \cite{paulson-blanchette-2010}.
Codatatypes being a recent addition to Isabelle
\cite{blanchette-et-al-2014-impl}, benchmarks are somewhat hard to come by. We
included the theory files from the Isabelle distribution (Distro) and the \emph{Archive
of Formal Proofs} (AFP) \cite{klein-et-al-afp} that define codatatypes falling
within the supported fragment. We also included two unpublished theories by
Peter Gammie and Andreas Lochbihler (\gandl), about Bird and Stern--Brocot trees.
To also exercise the the support
for datatypes, the benchmarks are complemented by theories about various list
and tree data structures. The theory files were selected before running the
experiments. The experimental data is publicly available \cite{our-eval-data}.
